---
title: "linear model from Web"
author: "Kimberly Orantes"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The ARM v. SIMS scatterplot shows a positive correlation between the two numerical variables. The scatterplot has a relatively consistent bond with of approximately -4 and the standard deviation of the data could be equal to approximately 1.  
   
### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation shown is 0.6860073.  
  
### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation of the line is: SIMS = 0.054563*(ARM) - 4.095160  
Our adjusted R-squared is 0.467. This indicates that ARM variable explains less than half of the variation of the SIMS data. This reduces the error of the mean model of the equation by 46.7%. The calculated residual standard error of the data is 1.226. This is the measure of the deviation from our regression line.  
  
#### Predict at target point

```{r}
mydata= data.frame(GRIP=94, ARM=88)
```

```{r}
predict(model.1,mydata, interval="confidence")
```


#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This scatter plot is trending up to the right of the graph, indicating a positive linear correlation.  
  
### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
  
The correlation is 0.6398458 which is smaller than the SIMS~ARM correlation of 0.6860073. It is a 0.0461615 difference.  
  
### Inferential  (Build model.2)
  
```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

The equation of the line is SIM = 0.045463*(GRIP) - 4.809675.  
The adjusted R-squared is 0.4094. This indicates that the GRIP variable explains less than half of the variation of the SIMS data. This reduces the error of the mean model of the equation by 40.9%. The calculated residual standard error of the data is 1.295, which is slightly greater than SIMS~ARM residual standard of error of 1.226. This is the measure of the deviation from our regression line.  
  
#### predict model.2 at target point

```{r}
predict(model.1,mydata, interval="confidence")
```
  
Here when GRIP is 94 and the prediction of SIMS is -0.5361543.  
  
#### now add the model fit to our plot for model.2
  
```{r}
basicNT <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNT + geom_point() + geom_smooth(method=lm)
``` 

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

